### 2022-06-09 manuscript.tex
Merge pull request #232 from SORTEE-Github-Hackathon/RCO-box-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/024357f04df193fe87662943d6e0029321eca2a5.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/024357f04df193fe87662943d6e0029321eca2a5/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2470979213

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/397be525b3f7dd06eb5e7e570a461d840fcb5a26/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/397be525b3f7dd06eb5e7e570a461d840fcb5a26}{SORTEE-Github-Hackathon/manuscript@397be52}
on June 9, 2022.

@@

\textbf{repository}: Commonly shortened to ``repo'', a repository is a collection of files (\emph{e.g.}, a directory) tracked by Git. Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users. \\

@@

\textbf{branch}: A git branch is an alternative line of development for a project (repository). Branches allow to add new features or modifications to the project without affecting the main part of the project. Development branches can be created at any point in time and work on each branch can continue independently. Branching is useful for testing out new ideas (both code and text) which may or may not eventually get integrated into the main branch of the project. Branches can also be used to isolate contributions of multiple contributors. Each person working on their own branch eliminates problems that may arise if conflicting edits are \textbf{pushed} to the same remote branch. Changes in a development branch can be \textbf{merged} into the main branch via \textbf{pull requests}. Branches can only be made by those who are given access to the project \textbf{repository}. \\

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/024357f04df193fe87662943d6e0029321eca2a5/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/024357f04df193fe87662943d6e0029321eca2a5}{SORTEE-Github-Hackathon/manuscript@024357f}
on June 9, 2022.

@@

\textbf{repository}: Commonly shortened to ``repo'', a repository is a collection of files (\emph{e.g.}, a directory) tracked by Git. Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users. Repositories can be either ``local'' and saved on an individual's computer or ``remote'' and stored on the cloud via GitHub's web platform. \\

@@

\textbf{branch}: Git workflow timelines or repositories are analogous to trees, with a main working project and diverging branches that are pointers to changes during the development process. A git branch is an alternative line of development for a project (repository). Branches allow users to add new features or modifications to the project without affecting the main part of the project. Development branches can be created at any point in time and work on each branch can continue independently. Branching is useful for testing out new ideas (both code and text) which may or may not eventually get integrated into the main branch of the project. Branches can also be used to isolate contributions of multiple contributors. Each person working on their own branch eliminates problems that may arise if conflicting edits are \textbf{pushed} to the same remote branch. Changes in a development branch can be \textbf{merged} into the main branch via \textbf{pull requests}. Branches can only be made by those who are given access to the project \textbf{repository}. \\
